CODE CHECK

### 2020-01-31 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail

>>>>

- need publishers build up data science experts who can conduct checks?
- integration of software/data citation checks benefitial?
- bot-support and tools (linter)
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODE CHECK work for preprints? how? is a re-check required?
- risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- code check in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
